Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-02-21 article.rnw
Add a missing semantic newline.
Break some preamble code in the report into more statements.
Declare the list of species names as its own variable, for clarity.
Reorder the species in the coclassifcation matrix figures, to show patterns more clearly.

<<include=FALSE>>=
	source("r/post-process.R")
	source("r/brute-post-process.R")
	brute_data <- BruteData$new(
		"output/brute.data",
		c(
			"D. birchii",
			"D. pallidifrons",
			"D. pandora",
			"D. pseudoananassae",
			"D. simulans",
			"D. sulfurigaster"
		)
	)

@@

\pgfplotsset{%
	colormap={coclassification}{color=(white) color=(red)}
}
\colorlet{coclassification diagonal}{black!20}
\begin{figure}
	\centering
	\begin{subfigure}{\textwidth}
		\centering
		<<echo=FALSE>>=
			weighted_coclassification_kable(
				brute_data$weighted_col_coclassification_matrix,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Weighted coclassification of competitive effects (columns of the interaction matrix).}
		\label{fig:coclassification-cols}
	\end{subfigure}

@@

	\begin{subfigure}{\textwidth}
		\centering
		<<echo=FALSE>>=
			weighted_coclassification_kable(
				brute_data$weighted_row_coclassification_matrix,
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Weighted coclassification of competitive responses (rows of the interaction matrix).}
		\label{fig:coclassification-rows}
	\end{subfigure}

>>>>

<<include=FALSE>>=
	source("r/post-process.R")
	source("r/brute-post-process.R")

	species_names <- c(
		"D. birchii",
		"D. pallidifrons",
		"D. pandora",
		"D. pseudoananassae",
		"D. simulans",
		"D. sulfurigaster"
	)
	species_output_order <- c(4,3,1,2,6,5)

	brute_data <- BruteData$new("output/brute.data", species_names)

@@

\pgfplotsset{%
	colormap={coclassification}{color=(white) color=(red)}
}
\colorlet{coclassification diagonal}{black!20}
\begin{figure}
	\centering
	\begin{subfigure}{\textwidth}
		\centering
		<<echo=FALSE>>=
			weighted_coclassification_kable(
				brute_data$weighted_col_coclassification_matrix[species_output_order,species_output_order],
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Weighted coclassification of competitive effects (columns of the interaction matrix).}
		\label{fig:coclassification-cols}
	\end{subfigure}

@@

	\begin{subfigure}{\textwidth}
		\centering
		<<echo=FALSE>>=
			weighted_coclassification_kable(
				brute_data$weighted_row_coclassification_matrix[species_output_order,species_output_order],
				colourmap="coclassification", diagonal_colour="coclassification diagonal"
			)
		@
		\caption{Weighted coclassification of competitive responses (rows of the interaction matrix).}
		\label{fig:coclassification-rows}
	\end{subfigure}
